Higher-Order unification for free!

### 2024-07-01 paper/main.tex
forall x:A, Decision (P x) in parentheses
an Higher -> a Higher

\begin{coqcode}
Instance fin_fin: ~$\forall$~n, Finite (fin n).             (* r1 *)
Instance nfact_dec: ~$\forall$~n nf, Decision (nfact n nf). (* r2 *)
Instance forall_dec: ~$\forall$~A P, Finite A ~$\to$~            (* r3 *)
  ~$\forall$~x:A, Decision (P x) ~$\to$~ Decision (~$\forall$~x:A, P x).
\end{coqcode}

@@

In order to implement such a search in Elpi, we shall describe the encoding
of Coq terms and then the encoding of instances as rules.
Elpi comes equipped with
an Higher-Order Abstract Syntax (HOAS~\cite{10.1145/53990.54010}) datatype of
Coq terms, called \elpiIn{tm}, that includes (among others) the following
constructors:

>>>>

\begin{coqcode}
Instance fin_fin: ~$\forall$~n, Finite (fin n).             (* r1 *)
Instance nfact_dec: ~$\forall$~n nf, Decision (nfact n nf). (* r2 *)
Instance forall_dec: ~$\forall$~A P, Finite A ~$\to$~            (* r3 *)
  ~($\forall$~x:A, Decision (P x)) ~$\to$~ Decision (~$\forall$~x:A, P x).
\end{coqcode}

@@

In order to implement such a search in Elpi, we shall describe the encoding
of Coq terms and then the encoding of instances as rules.
Elpi comes equipped with
a Higher-Order Abstract Syntax (HOAS~\cite{10.1145/53990.54010}) datatype of
Coq terms, called \elpiIn{tm}, that includes (among others) the following
constructors:
